Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2020-10-29 theory.tex
Adding r1/r2 information

>>>>

The parameters $r_1$ and $r_2$ are the separation radii of the enriched material
(here ${}^{235}\mathrm{U}$ vs. ${}^{238}\mathrm{U}$), $r_1$ being the withdrawal
radius for the lighter isotope and $r_2$ for the heavier isotope. R\"aetz's
two-shell model looks for optimal values between these two, as defined from
the hydrodynamic equations. The radii ratio is optimized using the following relationship:

\begin{equation}
    \max\{[1-(\frac{r_1}{r_2})^2]^2 \times [ \ln(\frac{r_2}{r_1})]^{-1}\}
\end{equation}

The ratio can further be constrained by approximating $r_2$ as being very close
to the inner centrifuge wall with radius $a$:

\begin{equation}
    (\frac{r_1}{r_2}) \approx (\frac{r_1}{a}) = \sqrt{1 - \frac{2RT}{M}(\ln x)\frac{1}{v_{a}^{2}}}
\end{equation}

Here the gas constants are mass, $M$, temperature $T$, universal gas constant, $R$,
and the pressure ratio, $x$ (typically $1000:1$).
This relationship is valid when $v_a > 380 \frac{\mathrm{m}}{\mathrm{s}}$.
Otherwise, the relationship can be approximated ${\frac{r_1}{r_2} \approx 0.534 \mid v_a \leq 380} \frac{\mathrm{m}}{\mathrm{s}}$.
